Plot responses to model covariates to inform threshold choices for VOCC

### 2019-08-02 analysis/VOCC/3-variable-response-plots.Rmd
minor tweaks to 3-variable-response-plots.rmd

# # Species run so far...
# species <- "Pacific Cod"
species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"

@@

Dissolved O2 plots
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
# covariates <- ""
try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

@@

model_list <- list(
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
  do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0,8)) + ggtitle(names(model_list[i]))
}
print(do_plots)
```

@@

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")
  #d[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")
  temp_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Temperature", xlimits = c(2,10)) + ggtitle(names(temp_model_list[i]))
}
print(temp_plots)
```

@@

```{r}
d <- list()
depth_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  d[[i]] <- time_varying_density(depth_model_list[[i]], predictor = "depth")
  d[[i]]$x <- exp(d[[i]]$x)
  depth_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Depth", xlimits = c(0,1000)) + ggtitle(names(depth_model_list[i]))
}
print(depth_plots)
```

>>>>

# # Species run so far...
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"

@@

Dissolved O2 plots
```{r}
rm(
  adult_survey1, imm_survey1,
  adult_survey4, imm_survey4,
  adult_survey16, imm_survey16
)
priors <- TRUE
# covariates <- ""

try({
  survey <- c("SYN QCS", "SYN HS", "SYN WCVI", "SYN WCHG")
  model_ssid <- c(1, 3, 4, 16)
  ssid_string <- paste0(model_ssid, collapse = "n")

  adult_survey_all <- readRDS(paste0(
    "data/", spp,
    "/mod-mat-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))

  imm_survey_all <- readRDS(paste0(
    "data/", spp,
    "/mod-imm-biomass-", spp, "-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
  ))
})
if (!exists("adult_survey_all")) adult_survey_all <- NULL
if (!exists("imm_survey_all")) imm_survey_all <- NULL

try({
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")

@@

model_list <- list(
  adult_survey_all=adult_survey_all, imm_survey_all=imm_survey_all,
  adult_survey1 = adult_survey1, imm_survey1 = imm_survey1,
  adult_survey4 = adult_survey4, imm_survey4 = imm_survey4,
  adult_survey16 = adult_survey16, imm_survey16 = imm_survey16
)

@@

```{r}
d <- list()
do_plots <- list()
for (i in seq_len(length(model_list))) {
  d[[i]] <- time_varying_density(model_list[[i]], predictor = "do_mlpl")
  do_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Dissolved O2", xlimits = c(0,8)) + ggtitle(paste(species, names(model_list[i])))
}
print(do_plots)
```

@@

```{r}
d <- list()
temp_plots <- list()
for (i in seq_len(length(temp_model_list))) {
  d[[i]] <- time_varying_density(temp_model_list[[i]], predictor = "temp")
  #d[[i]] <- fixed_density(temp_model_list[[i]], predictor = "temp")
  temp_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Temperature", xlimits = c(2,10)) +
    ggtitle(paste(species,names(temp_model_list[i])))
}
print(temp_plots)
```

@@

```{r}
d <- list()
depth_plots <- list()
for (i in seq_len(length(depth_model_list))) {
  d[[i]] <- time_varying_density(depth_model_list[[i]], predictor = "depth")
  d[[i]]$x <- exp(d[[i]]$x)
  depth_plots[[i]] <- plot_mountains(d[[i]], variable_label = "Depth", xlimits = c(0,1000)) + 
    ggtitle(paste(species, names(depth_model_list[i])))
}
print(depth_plots)
```
